
# Using the Package in R (Developers Only) {#packageinR}

As this is a private package, this section is for developers only. If you would like to discuss development of the package, please contact either:

Amin Adibi: amin.adibi@ubc.ca

Mohsen Sadatsafavi: mohsen.sadatsafavi@ubc.ca

## Installation

If you do not have R installed on your computer, please go to [Appendix 1](#appendix1). Once you have R installed, you can install the **framinghamPredictor** package as per the instructions below:

### Windows 7 or Later {-}
1. Download and Install the latest version of R from [https://cran.r-project.org/bin/windows/base/](https://cran.r-project.org/bin/windows/base/)
2. Download and Install R Studio from [https://www.rstudio.com/products/rstudio/download/](https://www.rstudio.com/products/rstudio/download/)

3. Using either an R session in Terminal or in R Studio, install the package `devtools`:

```{r, eval=FALSE, echo=TRUE}
install.packages('devtools')
```

4. Install `framinghamPredictor` from GitHub:

Note: This package has been set to private.

```{r, eval=FALSE, echo=TRUE}
devtools::install_github('resplab/framinghamPredictor')
```

### Mac OS Sierra and Later {-}
1. Download and Install the latest version of R from [https://cran.r-project.org/bin/macosx/](https://cran.r-project.org/bin/macosx/)
2. Download and Install R Studio from [https://www.rstudio.com/products/rstudio/download/](https://www.rstudio.com/products/rstudio/download/)

3. Using either an R session in Terminal or in R Studio, install the package `devtools`:

```{r, eval=FALSE, echo=TRUE}
install.packages('devtools')
```

4. Install epicR from GitHub:

```{r, eval=FALSE, echo=TRUE}
devtools::install_github('resplab/epicR')
```


### Ubuntu 16.04 and Later {-}

1. Install R if you don't have it installed already. See [Appendix 1](#appendix1) for installation guide.

2. Download and Install R Studio from [https://www.rstudio.com/products/rstudio/download/](https://www.rstudio.com/products/rstudio/download/)

3. Using either an R session in Terminal or in R Studio, install the package `devtools`:

```{r, eval=FALSE, echo=TRUE}
install.packages ('devtools')
```

4. Install `framinghamPredictor` from GitHub:

```{r, eval=FALSE, echo=TRUE}
devtools::install_github('resplab/framinghamPredictor')
```

```{r chunk-label, eval = FALSE, echo = TRUE}
install.packages("devtools")
devtools::install_github("resplab/framinghamPredictor")
```

## Running the Model

Now that you have installed `framinghamPredictor`, you can load the library:

```{r, eval = TRUE, echo = TRUE}
library(framinghamPredictor)
```

There should be the default input predictors which come preloaded:

```{r, eval = TRUE, echo = TRUE}
print(sample_predictors)
```

To run the model, you can use these `sample_predictors`, or adjust them yourself:

```{r, eval = FALSE, echo = TRUE}
make_predictions(resp_var="fev1", predictors=sample_predictors)
```
