
# Using the Package as an API (PRISM)

PRISM (Programmable Interface for Simulation/Statistical Models) is a package which provides a user-friendly API interface in R for clinical prediction and decision analytics models hosted on UBC PRISM cloud.

For more information, the PRISM package can be found on GitHub at [PRISM on  GitHub](https://github.com/resplab/prism).

## API in R/Javascript/Python/Bash {#api-in-r}

To get started, you will need to install a few packages:

```{r, eval=TRUE, echo=FALSE}
source("R/addHTML.R")
addHTML("install.html", section = 5, codeChunk = TRUE)
```

The next step is to get an API key. For now, we will be giving out API keys on a case-by-case basis, so please email either:

Amin Adibi: amin.adibi@ubc.ca

Mohsen Sadatsafavi: mohsen.sadatsafavi@ubc.ca

### Setting the Input {-}

To run the model, you can either use the default input, or set your own input. To see what the default input is, you can use the following `POST` call:

```{r, eval=TRUE, echo=FALSE}
addHTML("get-default-input.html", section = 5, codeChunk = TRUE)
```

### Running the Model {-}

To run the model with the default input, you can use the following `POST` call:

```{r, eval=TRUE, echo=FALSE}
addHTML("post-prism.html", section = 5, codeChunk = TRUE)
```

Now, the input for the `framinghamPredictor` package is quite large, so we won't print all the input options here. You may change as many of the default inputs as you like. I have highlighted below a few of the more common input parameters you might want to adjust:

```{r, eval=TRUE, echo=FALSE}
addHTML("post-prism2.html", section = 5, codeChunk = TRUE)
```

### Plots

When you call `model_run`, some plots are created from the data. To view these plots in `R`, you will need to use the `draw_plots` function. To download the plots via command line, you will need to use the `session_id`, which is returned by the `prism_model_run` function along with the data results. 

```{r, eval=TRUE, echo=FALSE}
addHTML("get-prism-plots.html", section = 5, codeChunk = TRUE)
```